---
title: "OECDPLOT REFERENCE MANUAL"
documentclass: report
fontsize: 11pt
classoption: oneside
geometry: verbose,letterpaper,tmargin=25mm,bmargin=25mm,lmargin=20mm,rmargin=20mm
subparagraph: true
output: 
  pdf_document: 
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: true
    latex_engine: pdflatex
    md_extensions: -autolink_bare_uris
---

```{r setup, cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE, tidy = FALSE}
knitr::opts_chunk$set(message = F, error = F, warning = F, comment = NA, fig.align = 'center', dpi = 100, fig.width=7.0, fig.height=4.0, tidy = F, cache.path = 'book_cache/', fig.path = 'book_figures/', dev = 'cairo_pdf')
```

\pagenumbering{gobble}
<!--Cover illustration-->
\ThisLLCornerWallPaper{1}{cover.pdf}
\begin{center} \end{center} <!--un truco para que no se superponga con la pag2-->
\cleardoublepage

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\begin{titlepage}
{\sffamily 
	\begin{center}
		\vspace*{\fill}
		\HRule \\[0.4cm]{
		\huge \bfseries OECDPLOT REFERENCE MANUAL}\\ [0.4cm]
		\HRule \\[1.5cm]
		%Authors
		\begin{minipage}{0.9\textwidth}
		\begin{center}
		\large
		MAURICIO VARGAS SEP\'ULVEDA
		\end{center}
		\end{minipage}
	\vfill
	\end{center}}
\end{titlepage}
\setcounter{page}{2}
\setlength\parindent{0pt} <!-- Removes all indentation from paragraphs-->
\renewcommand{\labelenumi}{\alph{enumi}.} <!-- Make numbering in the enumerate environment by letter rather than number (e.g. section 6)-->
\newpage

\textbf{OECDPLOT REFERENCE MANUAL}

Mauricio Vargas Sep\'ulveda

This version was published on `r Sys.Date()`.

\newpage
\tableofcontents
\newpage

\pagenumbering{arabic}
\setcounter{page}{1}

\chapter*{What to expect from this book}
\addcontentsline{toc}{chapter}{What to expect from this book}

This is a technical book. The book aims to get straight to the point, and the writing style is similar to a recipe with detailed instructions. It is assumed that you know the basics of R and that you want to learn to create beautiful plots according to OECD style rules.

Every chapter is self contained. You can read the whole book or go to a chapter or section of your interest, and we are sure that it will be easy to understand the instructions and reproduce our examples without reading the earlier chapters.

\newpage

```{r child = '01_Barplot.Rmd', eval = T}
```

```{r child = '02_Scatterplot.Rmd', eval = T}
```

```{r child = '03_MaxMin.Rmd', eval = T}
```

```{r child = '04_Shortcuts.Rmd', eval = T}
```

```{r child = '05_WhatIf.Rmd', eval = T}
```

\newpage

\thispagestyle{empty}
\pagecolor{mypurple}\afterpage{\nopagecolor}

\null
\vfill
