# Min-max plots

We will work towards creating the area plot below. We will take you from a basic bar plot and explain all the customisations we add to the code step-by-step.

This plot is build by adding _layers_ of different geoms, using the `geom_line()` and `geom_point()` functions. The first one add the vertical grey line behind the dots, and the second adds the overlaying points. Defining the shape parameter here adds a visual aid to make it easier to differentiate the different values.

```{r maxmin_final, echo = FALSE}
library(oecdplot)
library(ggplot2)

load_oecd_fonts()

p <- ggplot(pta, aes(x = country, y = pct_pta / 100)) +
  geom_line(colour = "grey") +
  geom_point(
    aes(shape = category),
    colour = oecd_clrs(n = 1, option = "darkblue"),
    size = 3
  ) +
  theme_oecd() +
  scale_y_continuous(labels = scales::percent) +
  labs(
    x = "Country",
    y = "%",
  )
p
```

## Basic graph

You can use fonts such as Arial Narrow within `ggplot2`. This package allows that with a dedicated function. The first thing to do is load in the libraries and data, as below:

```{r minmax_pkgs}
library(oecdplot)
library(ggplot2)

load_oecd_fonts()
```

We will be working with the `pta` dataset, which is included in the package.

```{r minmax_data}
pta
```

To initialise a plot we tell ggplot that `pta` is our data, and specify the variables on each axis. We then instruct ggplot to render this as an bar plot by adding the `geom_line()` and `geom_point()` functions. The colour argument is outside `aes()` in order to use the same colour for each figure.

```{r maxmin_1}
p <- ggplot(pta, aes(x = country, y = pct_pta / 100)) +
  geom_line(colour = "grey20") +
  geom_point(
    aes(shape = category),
    colour = oecd_clrs(n = 1, option = "darkblue"),
    size = 3
  )
p
```

## Adjusting theme

We can change the overall look of the graph using themes. We'll start using a simple theme customisation by adding `theme_oecd() ` after `ggplot()`.

```{r maxmin_2}
p <- p +
  theme_oecd()
p
```

## Adjusting axis scale

To change the scale to percentage, we can use the `percent()` function from the `scales` package, which comes with `ggplot2`.

```{r maxmin_3}
p <- p +
  scale_y_continuous(
    labels = scales::percent,
    expand = c(0,0),
    limits = c(0,1)
  )
p
```

## Adding labels

To obtain the plot from the start of this section, we use the `labs()` function.

```{r maxmin_4}
p <- p +
  labs(
    x = "Country",
    y = "%"
  )
p
```
