# Shortcuts

We will work towards creating different plots by using shortcut functions within
this package.

## Column plot

Simple column plot:
```{r sc1}
oecd_col(data = pta, x = country, y = pct_pta,  colour = category)
```

Stacked column plot:
```{r sc2}
oecd_col(data = pta, x = country, y = pct_pta, colour = category, stacked = T)
```

Stacked column plot with y-axis as percentage:
```{r sc3}
pta2 <- pta
pta2$pct_pta <- pta2$pct_pta / 100
oecd_col(data = pta2, x = country, y = pct_pta, colour = category) +
  scale_y_continuous(labels = scales::percent, expand = c(0,0))
```

Faceted column plot with y-axis as percentage:
```{r sc4}
pta2 <- pta
pta2$pct_pta <- pta2$pct_pta / 100

oecd_col(data = pta2, x = country, y = pct_pta, colour = category,
         facet = category) +
  scale_y_continuous(labels = scales::percent, expand = c(0,0))
```

## Line plot

Simple column plot:
```{r sl1}
oecd_line(pta, x = country, y = pct_pta, colour = category, group = category)
```

Faceted line plot:
```{r sl2}
oecd_line(pta,
  x = country, y = pct_pta, colour = category, group = category,
  facet = category
)
```

Faceted line plot with custom ordering:
```{r sl3}
oecd_line(pta,
  x = country, y = pct_pta, colour = category, group = category,
  facet = category, facet_ncol = 1
)
```

## Scatterplot

Simple scatterplot:
```{r sp1}
oecd_point(pta, x = country, y = pct_pta, colour = category, group = category)
```

Faceted scatterplot:
```{r sp2}
oecd_point(pta,
  x = country, y = pct_pta, colour = category, group = category,
  facet = category
)
```

Faceted line plot with custom ordering:
```{r sp3}
oecd_point(pta,
  x = country, y = pct_pta, colour = category, group = category,
  facet = category, facet_ncol = 1
)
```

Options specific to scatterplots:
```{r sp4}
oecd_point(pta,
  x = country, y = pct_pta, colour = category, group = category,
  facet = category, facet_ncol = 1, size = log(pct_pta)
)
```

# Max-min plot

Simple max-min plot:
```{r sm1}
oecd_maxmin(pta, x = country, y = pct_pta, colour = category, group = category)
```

Faceted max-min plot:
```{r sm2}
oecd_maxmin(pta,
  x = country, y = pct_pta, colour = category, group = category,
  facet = category
)
```

Faceted max-min plot with custom ordering:
```{r sm3}
oecd_maxmin(pta,
  x = country, y = pct_pta, colour = category, group = category,
  facet = category, facet_ncol = 1
)
```
