# What If?

## Exporting plots for official publication

Suppose you have the next plot.

```{r whatif_emf_1}
library(ggplot2)
library(oecdplot)

load_oecd_fonts()

ggplot(data = pta, aes(x = country, y = pct_pta / 100, fill = category)) +
  geom_col(position = "dodge2", width = 0.7) +
  theme_oecd() +
  scale_fill_oecd_d(option = "darkblue", direction = -1) +
  scale_y_continuous(labels = scales::percent, expand = c(0,0)) +
  facet_wrap(~category, ncol = 1) +
  labs(
    x = "Country",
    y = "%"
  )
```

We would only need to use the `save_oecd_chart()` function which already provides
PAC-compatible aesthetic elements including dimensions and formats.

```{r whatif_emf_2, eval = FALSE}
save_oecd_chart(
  file_name = "Figure 1",
  plot = last_plot(),
  folder = "my_folder/",
  size = "1/2",
  plot_title = "Figure 1. Regional disparities in protected terrestrial areas, 2017",
  plot_note = "Protected terrestrial areas refers to all protected areas recorded 
   in the World Database on Protected Areas (WDPA)",
  plot_source = "OECD calculations based World Database on Protected Areas (WDPA). 
   OECD (2020), OECD Regional Statistics (database)",
  statlink_create = TRUE,
  statlink_dataframe = pta,
  statlink_filename = "pta",
  box = FALSE,
  custom_size = NULL,
  format = "emf"
)
```

In the code above we can also pass `format = c("png","emf")` to create two files
at the same time.

## Trailing and leading spaces in the plotting area

Consider the next plot, where we already applied the OECD theme and formatted
the labels as percentage.

```{r whatif_whitespace_1}
library(dplyr)
library(tidyr)
library(ggplot2)
library(oecdplot)

load_oecd_fonts()

pta2 <- pta %>% 
  filter(category == "Country Value") %>% 
  mutate(pct_non_pta = 100 - pct_pta) %>% 
  pivot_longer(pct_pta:pct_non_pta) %>% 
  mutate(value = value / 100)

pta2_plot <- pta2 %>%
  ggplot(aes(x = value, y = country)) +
  geom_col(aes(fill = name), width = 0.4) +
  scale_fill_oecd_d() +
  labs(y = "Country", x = "%") +
  theme_oecd(base_x_axis_angle = 0)+
  scale_x_continuous(
    labels = scales::percent_format(accuracy = 1)
  )

pta2_plot
```

One option to remove the whitespace in the plot is to use the `expand` 
parameter, in order to start from the (0,0) coordinate.

```{r whatif_whitespace_2}
pta2_plot + 
  scale_x_continuous(
    expand = c(0,0),
    labels = scales::percent_format(accuracy = 1)
  )
```

This plot has a problem, the "100%" label is outside the margins, which is
covered in then next what-if.

## The x-axis contains off-margin labels

Consider the next plot, where we added different adjustments, such as
the x-axis labels rotation.

```{r whatif_offmargin_3}
library(dplyr)
library(tidyr)
library(ggplot2)
library(oecdplot)

load_oecd_fonts()

pta2 <- pta %>% 
  filter(category == "Country Value") %>% 
  mutate(pct_non_pta = 100 - pct_pta) %>% 
  pivot_longer(pct_pta:pct_non_pta) %>% 
  mutate(value = value / 100)

pta2_plot <- pta2 %>%
  ggplot(aes(x = value, y = country)) +
  geom_col(aes(fill = name), width = 0.4) +
  scale_fill_oecd_d() +
  labs(y = "Country", x = "%") +
  theme_oecd(base_x_axis_angle = 0)+
  scale_x_continuous(
    expand = c(0,0), 
    labels = scales::percent_format(accuracy = 1)
  )

pta2_plot
```

In this case, we can alter the x-axis scale options to define the range
to go from 0 to 1.01 (or 1.02-1.05).

```{r whatif_offmargin_4}
pta2_plot +
  scale_x_continuous(
    expand = c(0,0), 
    limits = c(0,1.01),
    labels = scales::percent_format(accuracy = 1)
  )
```

An alternative solution could be rotating the labels.

```{r whatif_offmargin_5}
pta2_plot +
  theme_oecd(base_x_axis_angle = 30)
```

## Too many lines/columns

One option is to use ggplot2's `facet_wrap()`, as in the next example.

```{r}
ggplot(pta %>% filter(country %in% c("CAN", "USA", "MEX"))) +
  geom_col(aes(x = category, y = pct_pta), fill = oecd_clrs()[1]) +
  facet_wrap(~country)
```

